Tutorial: Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2023-08-29 manuscript/manuscript.tex
Formatted some codeblock comments to use python format

\begin{lstlisting}[style=python]
col = 'dTSsix_dens'
def select(traj, sel):
    'Slice a Trajectory by selection mask.'
    return traj.atom_slice(traj.top.select(sel))
# we multiply by 10 to convert nm to Angstrom.
compl_x = select(compl.struct, biotin_mask).xyz[0] * 10.
biotin_x = select(biotin.struct, biotin_mask).xyz[0]*10.
aligned = compl.struct[:].superpose(strept.struct, \
    atom_indices=strept.struct.top.select(strept_mask))
aligned = select(aligned, biotin_mask)
strept_x = aligned.xyz[0] * 10.

@@

\begin{lstlisting}[style=python]
def select(traj, sel):
	'Slice a Trajectory by selection mask.'
	return traj.atom_slice(traj.top.select(sel))
### Load GIST data
compl = gt.gist.load_gist_file(
	'complex/gist/gistoutlong.dat', 
	struct='complex/gist/gist_nowat.pdb')
### Define ligand atoms and find voxels around them
rmax = 3.5
biotin_mask = 'resname BTN and not element H'
btn = select(compl.struct, biotin_mask).xyz[0] * 10.
ind, _, _ = compl.distance_to_spheres(btn, rmax)

>>>>

\begin{lstlisting}[style=python]
col = 'dTSsix_dens'
def select(traj, sel):
    # Slice a Trajectory by selection mask.
    return traj.atom_slice(traj.top.select(sel))
# we multiply by 10 to convert nm to Angstrom.
compl_x = select(compl.struct, biotin_mask).xyz[0] * 10.
biotin_x = select(biotin.struct, biotin_mask).xyz[0]*10.
aligned = compl.struct[:].superpose(strept.struct, \
    atom_indices=strept.struct.top.select(strept_mask))
aligned = select(aligned, biotin_mask)
strept_x = aligned.xyz[0] * 10.

@@

\begin{lstlisting}[style=python]
def select(traj, sel):
	# Slice a Trajectory by selection mask.
	return traj.atom_slice(traj.top.select(sel))
### Load GIST data
compl = gt.gist.load_gist_file(
	'complex/gist/gistoutlong.dat', 
	struct='complex/gist/gist_nowat.pdb')
### Define ligand atoms and find voxels around them
rmax = 3.5
biotin_mask = 'resname BTN and not element H'
btn = select(compl.struct, biotin_mask).xyz[0] * 10.
ind, _, _ = compl.distance_to_spheres(btn, rmax)
